EE454 Project 1 Report

### 2015-09-24 p1/report/latex/draft.tex
Commit

\documentclass[11pt,english]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage[toc,page]{appendix}
\usepackage{color}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\usepackage{titlesec}
\graphicspath{ {../} }

@@

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=Octave,                 % the language of the code
  otherkeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

@@

\subsection{Purpose}
The purpose of this project was to implement a pre-trained convolutional neural network (CNN) using MATLAB.  The CNN is composed of layers - each layer performs an operation on a set of input matrices and produces a corresponding output matrix.  When these layers are composed together, they produce a network; the input of this network is an image, and the output of this network is a vector of classification probabilities.

\subsection{Operations}

\subsubsection{Image Normalization}

\lstinputlisting[frame=single]{../../matlab/convolve.m}

@@

Intermediate output generated by the CNN is included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.  The images can be produced by running `demo.m.'

Observation of the output from each layer is consistent with the project description.  Normalization produces an image with scaled pixel values but is relatively unchanged.  Convolution produces a set of images with different feature sets extracted.  The ReLu produces an image with a 0 threshold (MATLAB's imagesc command slightly changes the output image because the range of the pixel values in the image changes).  Max Pooling reduces the size of the image by a factor of (nxn) and has the effect of making the previous image look more ``blocky'' via down-sampling.  Finally, we have the fully-connected layer and the soft max layer which produce a vector of classification probabilities from the image which are represented by the bar graph.

@@

		\textbf{Accuracy = 43.7\%}
\end{center}

@@

\subsection{Looking at the Top-k Highest Probabilities}
	The following subsection looks at how frequently an image's true class appears in one of the top-k ranked classes, as determined by probability scores sorted from highest to lowest.
\begin{center}
	\includegraphics[scale=0.8]{topktable}
	Note: Accuracy is the percentage of times that the correct object class appeared in the top-k ranked classes, as determined by probability scores sorted form highest to lowest. 
	~\\
\end{center}
\begin{center}
	\includegraphics[scale=0.8]{topkplot}
	~\\~\\
\end{center}
\textbf{Discussion:}
      We were very surprised to see the top-k classification plot follow an exponential distribution. This demonstrates that the probability estimations provided by the CNN are accurate. We expected the probability estimations to be an arbitrary metric, but looking at the logarithmic nature of the plot it is clear that the probabilities are very accurate.

>>>>

\documentclass[11pt,english]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage[toc,page]{appendix}
\usepackage{titlesec}
\graphicspath{ {../} }

@@

@@

@@

Intermediate output generated by the CNN is included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.

@@

		Accuracy = 43.7\%
\end{center}

@@

\subsection{Looking at the Top-k Highest Probabilities}
	The following subsection looks at how frequently an image's true class appears in one of the top-k ranked classes, as determined by probability scores sorted from highest to lowest.
\begin{center}
	\includegraphics[scale=0.8]{topktable}

\end{center}
	Note: Accuracy is the percentage of times that the correct object class appeared in the top-k ranked classes, as determined by probability scores sorted form highest to lowest. 
	~\\
\begin{center}
	\includegraphics[scale=0.8]{topkplot}
	~\\~\\
\end{center}
\textbf{Discussion:}
      We were very surprised to see the top-k classification plot follow a logarithmic distribution. This demonstrates that the probability estimations provided by the CNN are accurate. We expected the probability estimations to be an arbitrary metric, used to find reasonable classification for an image, but looking at the logarithmic nature of the plot it is clear that the probabilities are very accurate. In fact, when looking at the probabilities for the 10,000 images you will find that on average an images top-k probabilities sum up to the y value shown above. For example, the average max probabilities for the 10,00 images is .4425 and 43.71\% of the time the max probability is correct. Even more interesting, the average of the top 2 probabilities added together for each image is .6646 and the chance of the true class being associated with one of the top two highest probabilities in its probability vector .6591, as shown above.
